---
title: "Developing Data Products: Course Project"
author: "Ryan Till"
date: "November 11, 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Temperature Prediction

This app uses the airquality dataset from the datasets package in R to fit a regression model and predict the temperature (F) using predictors chosen by you. Note that this data set measures daily air quality in New York from May to September of 1973.

## Input

The predictors available for you to choose from are listed below.

- Ozone: mean ozone in parts per billion
- Solar.R: solar Radiation in Langleys
- Wind: average wind speed in miles per hour
- Month: the number of the month from May (5) to September (9)

Once selected, you'll be able to choose specific values for the active predictors and generate your own temperature prediciton.

## Output

When a predictor is selected, the app will generate a plot with the predicted temperature on the x-axis, the actual temperature on the y-axis and a line to help illustrate model fit. As other predictors are added or removed, this plot will be regenerated to either include or exclude them.  

Below the plot, the average error and your predicted temperature will be calculated.

## Example of Use

So, let's say for example that you've chosen to include Ozone and the Month as your predictors. In that case your plot would look like the one below.

```{r, plot example, fig.height=4, fig.width=5, fig.align='center'}
data('airquality')
my_data = airquality[complete.cases(airquality),]

fit = lm(Temp ~ Ozone + factor(Month), data = my_data)
avg_err = sqrt(sum(resid(fit)^2) / length(resid(fit)))
plot(predict(fit), my_data$Temp, 
     pch = 16, xlab = 'Predicted Temp', ylab = 'Actual Temp', 
     main = 'Predicted vs Actual Values')
abline(lm(my_data$Temp ~ predict(fit)))


vals = c(25, 6)
        
pred_df = data.frame(Ozone   = vals[1], 
                     Solar.R = 0,
                     Wind    = 0,
                     Temp    = 0,
                     Month   = vals[2],
                     Day     = 0)
        
pred_val   = round(predict(object = fit, newdata = pred_df))
pred_value = paste("Predicted Value: ", pred_val, sep = "")
```

Your average error would display as `r round(avg_err, 2)` and if you then set your values of Ozone and Month to 25 and 6 respectively, your predicted value would be calculated as `r pred_val`.

